The proposed bottle filling system (``System") solves the problem of rinsing, filling and packaging bottles in high speed with low operation cost. When compared to manual processes the advantage is clear in terms of economy but the System also meets more complex business requirements. In a paint manufactures, for example, several colors of paint are produced, bottled and packaged, but each paint cannot get mixed with the others.

Not only that, but typically black and white paint ship in larger bottles, while colored paint sells is smaller containers. The feeder of bottles of such machines must be able to comport containers of different sizes. The feeder of paint must also be able to be filled with different colors of paint. In the case of paint, the feeder must be cleaned so colors do not get mixed whenever the paint is changed. Other liquids have different requirements, such as toxicity removal or cleaning through chemical reactions.

Bottles flow from the feeder onto the conveyor. Once on the conveyor, the bottles are rinsed and proceed to the liquid filler. Once a predetermined amount of bottles reach the liquid filler, the liquid flows from the liquid feeder to the bottles. After it is filled the bottle must be caped and moved to a predetermined area. The process of moving may involve sorting or could be directly connected to the startup configuration of the feeders. The conveyor part System featured only fills the bottle. 

Safety wise, the system meets some requirements by making sure the main system always starts up in a safe state. Starting up in a safe state means that it will not start until the conveyor is empty. After a power loss or emergency shutdown, bottles will stay in the conveyor and they could be from the earlier stages of cleaning to filled. When starting up again, through retentive counters, the system knows some bottle were left behind and proceeds to move them to a designated area. 

The same process of moving objects to a designated area happens when shutting down the system normally. When instructed to shutdown, the main system immediately shuts down, but a shut down system powers on if there are bottles in the conveyor. Of course, red indicator lights are on whenever any of recovery, shutdown and main system are on.






